---
title: "geo2smoof"
author: "Jakob Richter"
output:
  html_document:
  toc: true
toc_float:
  collapsed: false
smooth_scroll: false
vignette: >
  %\VignetteIndexEntry{mlrHyperopt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, cache = FALSE}
set.seed(123)
knitr::opts_chunk$set(cache = TRUE, collapse = FALSE)
library(geo2smoof)
```

This Vignette is supposed to give you a short introduction and a glance at the key features of `geo2smoof`.
For updated information make sure to check the GitHub project page:

- [Project Page](https://github.com/jakob-r/geo2smoof/)
- Online documentation of [geo2smoof](https://jakob-r.github.io/geo2smoof/)

## Purpose

geo2smoof truns a elevation map into a function that returns the elevation for given coordinate input.
More precisely this package generates [smoof functions](https://github.com/jakobbossek/smoof) as these contain valuable meta information for each function.

## Example usage

### Raster

```{r}
alt_s = raster::getData('alt', country='SVN', mask = FALSE)
sf = convertRasterLayerToSmoof(raster.layer = alt_s)
getParamSet(sf)
sf(c(204,103))
plot2DNumeric(sf, render.levels = TRUE, n.samples = 200)
```

### Combining Multiple Raster

Generating a function out of the subsection of the alps:
```{r}
alt_d = raster::getData('alt', country='DEU')
alt_a = raster::getData('alt', country='AUT')
alt_c = raster::getData('alt', country='CHE', mask = FALSE)
alt_i = raster::getData('alt', country='ITA')
alt_all = do.call(raster::merge, list(alt_d, alt_a, alt_c, alt_i, alt_s))
alt_cropped = raster::crop(alt_all, raster::extent(7,16,45.5,47.8))
sf = convertRasterLayerToSmoof(raster.layer = alt_cropped)
getParamSet(sf)
plot2DNumeric(sf, render.levels = TRUE, n.samples = 200)
```

### Google Maps Elevation API

You can register for a free API-Key [here](https://developers.google.com/maps/documentation/elevation/get-api-key).
Afterwards you can save it using `saveGeo2SmoofConfig()` or write it manually in every call of `convertGoogleApiToSmoof()`.
We will not use an API-Key here and thus are limited to just a few calls
```{r}
lat.range = c(28.5, 27.5)
lon.range = c(86.5, 87.5)
gsf = convertGoogleApiToSmoof(lat.range = lat.range, lon.range = lon.range)
gsf(c(29,87))
plot2DNumeric(gsf, render.levels = TRUE, n.samples = 5)
```
